---
title: "Initiate.My"
output: html_document
date: "2025-02-07"
---

Question: I am curious to know which types content would gain the most followers, number of likes, comments, saves, & shares?

#Step 1: Uploading dataset
```{r}
library(readr)
tik_tok_data <- read_csv("~/Downloads/tik_tok_data.csv")
```

#Step 2: Exploring dataset
```{r}
str(tik_tok_data)
unique(tik_tok_data$`Content Description`) # There's an issue with the cases in the dataset; we have 18 categories
```

# Step 3: Data Cleaning of the Content Description
```{r}
library(dplyr)
library(stringr)

# Normalize and categorize content descriptions
tik_tok_data_clean <- tik_tok_data %>%
  mutate(
    `Content Description`= case_when(
      str_detect(tolower(`Content Description`), "supremacy") ~ "Malay Supremacy",
      str_detect(tolower(`Content Description`), "victimisation") ~ "Malay Victimisation",
      str_detect(tolower(`Content Description`), "anti[- ]?minorities") ~ "Anti-Minorities",
      str_detect(tolower(`Content Description`), "anti[- ]?migrant|refugees") ~ "Anti-Migrant/Refugees",
      str_detect(tolower(`Content Description`), "threat|incitement to violence") ~ "Threat/Incitement to Violence",
      str_detect(tolower(`Content Description`), "slur|verbal attack") ~ "Slurs/Verbal Attacks",
      str_detect(tolower(`Content Description`), "extremist symbol|panji hitam") ~ "Extremist Symbols",
      str_detect(tolower(`Content Description`), "antisemetic") ~ "Antisemitic",
      str_detect(tolower(`Content Description`), "glorification|sympathy") ~ "Glorification/Sympathy",
      str_detect(tolower(`Content Description`), "conspiracy") ~ "Conspiracy Theories",
      TRUE ~ `Content Description` # Default to original if not matched
    )
  )

unique(tik_tok_data_clean$`Content Description`) #Condensed to 10 categories
```

# Step 4: Analysis
## Step 4.1: Followers by content description
Anti migrant/refugees gets the most followers
```{r}
# Creating the table
followers_by_content_description<- tik_tok_data_clean %>% 
  group_by(`Content Description`) %>% 
  summarize(total_followers = sum(`Number of followers`, na.rm = TRUE)) %>% 
  arrange(total_followers)

# Printing the table
print(followers_by_content_description)

library(ggplot2)
library(scales)  # For numeric formatting

ggplot(followers_by_content_description, aes(x = reorder(`Content Description`, total_followers), y = total_followers)) +
  geom_col(fill = "steelblue") +
  coord_flip() +  # Flip for better readability
  scale_y_continuous(labels = comma) +  # Convert to numeric format
  labs(
    title = "Followers by Content Description",
    x = "Content Description",
    y = "Total Followers"
  ) +
  theme_minimal()
```

## Step 4.2: Likes by content description
Extremist symbols gets the most like
```{r}
# Creating the table
likes_by_content_description<- tik_tok_data_clean %>% 
  group_by(`Content Description`) %>% 
  summarize(total_likes = sum(`Number of likes`, na.rm = TRUE)) %>% 
  arrange(total_likes)

# Printing the table
print(followers_by_content_description)

library(ggplot2)
library(scales)  # For numeric formatting

ggplot(likes_by_content_description, aes(x = reorder(`Content Description`, total_likes), y = total_likes)) +
  geom_col(fill = "steelblue") +
  coord_flip() +  # Flip for better readability
  scale_y_continuous(labels = comma) +  # Convert to numeric format
  labs(
    title = "Likes by Content Description",
    x = "Content Description",
    y = "Total Likes"
  ) +
  theme_minimal()
```

## Step 4.3: Comments by content description
Anti-Minorities gets the most comments
```{r}
# Creating the table
comments_by_content_description<- tik_tok_data_clean %>% 
  group_by(`Content Description`) %>% 
  summarize(total_comments = sum(`Number of comments`, na.rm = TRUE)) %>% 
  arrange(total_comments)

# Printing the table
print(comments_by_content_description)

library(ggplot2)
library(scales)  # For numeric formatting

ggplot(comments_by_content_description, aes(x = reorder(`Content Description`, total_comments), y = total_comments)) +
  geom_col(fill = "steelblue") +
  coord_flip() +  # Flip for better readability
  scale_y_continuous(labels = comma) +  # Convert to numeric format
  labs(
    title = "Comments by Content Description",
    x = "Content Description",
    y = "Total Comments"
  ) +
  theme_minimal()
```

## Step 4.4: Save by content description
Malay supremacy gets the most saves
```{r}
# Creating the table
save_by_content_description<- tik_tok_data_clean %>% 
  group_by(`Content Description`) %>% 
  summarize(total_save = sum(`Number of saves`, na.rm = TRUE)) %>% 
  arrange(total_save)

# Printing the table
print(save_by_content_description)

library(ggplot2)
library(scales)  # For numeric formatting

ggplot(save_by_content_description, aes(x = reorder(`Content Description`, total_save), y = total_save)) +
  geom_col(fill = "steelblue") +
  coord_flip() +  # Flip for better readability
  scale_y_continuous(labels = comma) +  # Convert to numeric format
  labs(
    title = "Saves by Content Description",
    x = "Content Description",
    y = "Total Saves"
  ) +
  theme_minimal()
```

## Step 4.4: Shares by content description
Malay supremacy gets the most shares
```{r}
# Creating the table
shares_by_content_description<- tik_tok_data_clean %>% 
  group_by(`Content Description`) %>% 
  summarize(total_shares = sum(`Number of shares`, na.rm = TRUE)) %>% 
  arrange(total_shares)

# Printing the table
print(shares_by_content_description)

library(ggplot2)
library(scales)  # For numeric formatting

ggplot(shares_by_content_description, aes(x = reorder(`Content Description`, total_shares), y = total_shares)) +
  geom_col(fill = "steelblue") +
  coord_flip() +  # Flip for better readability
  scale_y_continuous(labels = comma) +  # Convert to numeric format
  labs(
    title = "Shares by Content Description",
    x = "Content Description",
    y = "Total Shares"
  ) +
  theme_minimal()
```

Conclusion:
1. Malay supremacy content will get you the most shares & saves
2. Anti-minorities will get you the most comments
3. Extremist symbols will get you the most likes
4. Anti migrant/refugees will get you the most followers (perhaps has the most)